White Dwarf Mergers on Adaptive Meshes\\ II. Nuclear Reactions

### 2017-09-25 papers/wdmerger_II/paper.tex
Update sponge discussion

As in Paper I, the region outside the WDs is filled with a low-density ambient
material with $\rho = 10^{-4}\ \text{g / cm}^{-3}$ whose composition and temperature is the
same as that of the WDs. Reactions in this region are unimportant, so for
computational efficiency, we disable all nuclear burning for zones that have
$\rho < 10^6\ \text{g / cm}^{-3}$ and $T < 10^8\ \text{K}$. We have confirmed that
the results do not depend on this choice. A sponge is applied to all gas at a distance
greater than $2.5 \times 10^9$ cm from the origin, which is just larger than the
initial location of the outer edges of the white dwarfs. The sponge damps out the
velocity in this region (see Paper I) to prevent spurious numerical error from dragging
down the global timestep. The density floor for the simulation is set
at $10^{-5}\ \text{g / cm}^{-3}$ and the temperature floor is $10^7$ K.

>>>>

As in Paper I, the region outside the WDs is filled with a low-density ambient
material with $\rho = 10^{-4}\ \text{g / cm}^{-3}$ whose composition and temperature is the
same as that of the WDs. Reactions in this region are unimportant, so for
computational efficiency, we disable all nuclear burning for zones that have
$\rho < 10^6\ \text{g / cm}^{-3}$ and $T < 10^8\ \text{K}$. We have confirmed that
the results do not depend on this choice. A sponge is applied to all gas of density
lower than $1\ \text{g / cm}^{-3}$. The sponge damps out the velocity in these zones
(see Paper I) to prevent spurious numerical error in low-density gas from dragging
down the global timestep. The density floor for the simulation is set
at $10^{-5}\ \text{g / cm}^{-3}$ and the temperature floor is $10^7$ K.
